Approximation as Differentiation

### 2025-03-26 notes.tex
C -> D.
Placeholder for FdVect.

\title{Approximation as Differentiation notes}
\maketitle

@@

Notions covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction and category of families $\Fam(C)$ (\secref{grothendieck})
\item category of $\LatGal$ of bounded lattices and Galois connections (\secref{galois})
\end{itemize}

>>>>

\title{Approximation as Differentiation}
\maketitle

@@

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful categories with biproducts:
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FdVect_k$ of finite-dimensional vector spaces over a field $k$ (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

### 2025-03-26 notes/sec/galois.tex
Assume C locally small.
secrefs.
Placeholder for FdVect.

\subsection{Category of bounded lattices and Galois connections}

@@

\subsection{Category $\Func{\LatGal^\op}{\CMon}$}

A presheaf $F: \LatGal^\op \to \CMon$ assigns to every bounded lattice $L$ a commutative monoid $F(L)$ and to
every Galois connection $f: L \to L'$ a commutative monoid homomorphism $F(f): F(L) \to F(L')$.
$\Func{\LatGal^\op}{\CMon}$ is the category of presheaves of commutative monoids on $\LatGal$.

>>>>

\subsection{Useful categories with biproducts}
\label{sec:categories-with-biproducts}

\subsubsection{Category of bounded lattices and Galois connections}
\label{sec:categories-with-biproducts:latgal}

@@

\subsubsection{Category of finite-dimensional vector spaces}
\label{sec:categories-with-biproducts:fdvect}

% \subsubsection{$\CMon$-valued presheaves over $\LatGal$}
%
% A presheaf $F: \LatGal^\op \to \CMon$ assigns to every bounded lattice $L$ a commutative monoid $F(L)$ and to
% every Galois connection $f: L \to L'$ a commutative monoid homomorphism $F(f): F(L) \to F(L')$.
% $\Func{\LatGal^\op}{\CMon}$ is the category of presheaves of commutative monoids on $\LatGal$.
